Growth model analysis

### 2017-12-13 manuscriptAnalysis/MS_Analysis.Rmd
Trying to fix lack of convergence in gr model

```{r p(detection)}
  ggPInt <- array2df(ddD$sims.list$pBetaInt, label.x = "est")

  ggPInt$chain <- rep(1:ddD$mcmc.info$n.chains, each = ddD$mcmc.info$n.samples/ddD$mcmc.info$n.chains)
  ggPInt$iter <- 1:as.numeric(ddD$mcmc.info$n.samples/ddD$mcmc.info$n.chains)

  ggplot(filter(ggPInt), aes(iter,est)) + 
    geom_point( aes(color=factor(chain)), size = 0.1 ) + 
    ylim(-1.5,1.5) + 
    facet_grid(d2+d4~d5+d3)

  p <- array2df(ddD$q50$pBetaInt, label.x = "est") %>%
    rename(est=est,species=d1,season=d2,river=d3,year=d4)
  ggplot(p, aes(year,invlogit(est))) +geom_point() + facet_grid(season ~ river + species)
  ggsave('figures/p.png')

@@

  # tmp <- dddD[[2]] %>%
  #          group_by(riverOrdered,year,season,section) %>%
  #          summarize( s = sum(enc) ) %>%
  #          filter( s == 0 )
  # table(tmp$riverOrdered,tmp$year,tmp$season)

@@

ggplot(d, aes(year,nAllFishP)) +
  geom_point() +
  geom_line() +
  labs( x = "Year", y = "Estimated count") +
#  ylim(0,2500) +
  theme_publication() +
  facet_grid(seasonGG ~ riverOrderedGG, scales = "free")

>>>>

```{r p(detection)}
  # ggPInt <- array2df(ddD$sims.list$pBetaInt, label.x = "est")
  # 
  # ggPInt$chain <- rep(1:ddD$mcmc.info$n.chains, each = ddD$mcmc.info$n.samples/ddD$mcmc.info$n.chains)
  # ggPInt$iter <- 1:as.numeric(ddD$mcmc.info$n.samples/ddD$mcmc.info$n.chains)
  # 
  # ggplot(filter(ggPInt), aes(iter,est)) + 
  #   geom_point( aes(color=factor(chain)), size = 0.1 ) + 
  #   ylim(-1.5,1.5) + 
  #   facet_grid(d2+d4~d5+d3)

  p <- array2df(ddD$q50$pBetaInt, label.x = "est") %>%
    rename(est=est,species=d1,season=d2,river=d3,year=d4)
  ggplot(p, aes(year,invlogit(est))) +geom_point() + facet_grid(season ~ river + species)

   ggsave('figures/p.png')

@@

# # of skunked sections    
  tmp <- dddD[[2]] %>%
           group_by(riverOrdered,year,season,section) %>%
           summarize( s = sum(enc) ) %>%
           filter( s == 0 )
  table(tmp$riverOrdered,tmp$year,tmp$season)

@@

ggplot(d, aes(year,nAllFishBySpeciesP)) +
  geom_point(aes(color=speciesGG)) +
  geom_line(aes(color=speciesGG)) +
  labs( x = "Year", y = "Estimated count") +
#  ylim(0,2500) +
  theme_publication() +
  facet_grid(seasonGG ~ riverOrderedGG, scales = "free")
